Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-02 manuscript.tex
Went through Sect 1, 2, 3 and did some small modif, updated the text according to Jessi's comments

%\documentclass[referee]{aa}
%
\usepackage{pdflscape} % or {lscape}
\usepackage{natbib}
%\usepackage{lscape}
\usepackage{wasysym}
\usepackage[varg]{txfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
\usepackage{longtable}

@@

\abstract
% Context, Aims, Methods, Results, Conclu (not mandatory)
{Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modeled CCF. Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
%
{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
%
{The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.}
%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels. In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.  We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
%
{When considering the real observations, the correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach. 
This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
The estimated uncertainties in the estimated RV's using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF. }
{XXX \jessi{It looks like we still need to add conclusions here}}
%
%{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.  Furthermore, the estimated uncertainties on the RV's and the asymmetry parameter are smaller in the SN setting.}
%The correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations. Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals. The precision on the estimated set of RV's, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN). We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RV's and the the asymmetry parameter are smaller than the one estimated with the Normal fit.

@@

When working with radial velocities (RV's), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}. 
Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are above the meter-per-second precision reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
%
It is therefore mandatory to better understand stellar signals and to develop methods to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique. This is even more true now that instrument like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should have the stability to detect such signals. However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging and false detections could plague the field.

@@

One of the most challenging stellar signal to characterize and to correct for is the signal induced by stellar activity. 
Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}. 
In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}. 
However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity can induce signals of a few \ms. This corresponds physically to variations smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.

In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}. The result of this operation gives us the cross-correlation function (CCF).  The CCF gives the spectrum's cross-correlation with the template as the template is shifted according to different RVs.
%
To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, the variations of the CCF barycenter are calculated. 
The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean. Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different moments of the CCF. Usually, the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.

@@

If an apparent RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}. 
%
It is therefore common now, that when fitting a Keplerian signal to a set of RVs to look for a planet, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
%
It is also common to add a Gaussian process to the model to account for the correlated noise induced by stellar activity. The hyperparameters of the Gaussian process can be trained on different activity indicators \citep{Haywood-2014,Rajpaul-2015}. It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated with the RV's but also for which we can obtain the best precision.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Figueira indicators of stellar activity + other}
Several indicators have been developed that are more sensitive to line asymmetry than the BIS SPAN. In \citet{Boisse-2011}, the authors develop $V_{span}$, which is the difference between the RV measured respectively by fitting a Normal density to the upper and the bottom part of the CCF. This CCF asymmetry parameter is shown to be more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
%
\citet{Figueira-2013} studied the use of two new indicators, bi-Gauss and $V_{asy}$. The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger than when using BIS SPAN, therefore allowing the detection of lower levels of activity. They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any of the previously proposed asymmetry indictors.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Outline of paper}
The paper is organized as follow. In Sec.~\ref{sec:2} we introduce the SN density, describe its applicability for modeling the CCF, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF. 
%
In Sec.~\ref{sec:31} we propose an expanded linear model used to correct the estimated RV's from the inferred stellar activity, which extends the linear models previously proposed for this purpose \citep{Dumusque:2017aa,Feng:2017aa}. 
%
In Sec.~\ref{sec:soap} the performance of the SN fit to the CCF is investigated using simulations coming from the Spot Oscillation And Planet (SOAP) 2.0 \citep{Dumusque-2014b}, followed by an analysis of real observations in Sec.~\ref{sec:4}.
%
Sec.~\ref{sec:5} considers derived error bars for the different estimated CCF parameters, and finally a discussion of the results and conclusions are included in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}, respectively.

@@

By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a clearer interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ provides an measure of the skewness of the SN. 
Along with the mean of the SN, we consider the median of the distribution as a measure of center, which is used in the proposed method.  See Table~\ref{tab:cp_values} for the medians of the SN densities displayed in Fig.~\ref{fig:SN.plot}.
%The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
%%
%\begin{equation} \label{eq:snmed}
%\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2}.
%\end{equation}
%

%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
\begin{center}
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|ccccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$  & Median \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667  	& 	-0.672\\
0	&	 0.000 	&	1.000	&	 0.000 	& 	0.000\\
2	&	 0.714	&	 0.491	&	 0.454 	& 	0.655\\
6	&	 0.787	&	 0.381	&	 0.891 	& 	0.674\\
10	&	 0.794	&	 0.370	&	 0.956 	& 	0.674\\
\hline
   \end{tabular}
   \caption{CP values $(\mu, \sigma^2, \gamma)$ along with the median corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$. Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{center}
\end{table}
%
Further details about the parametrization from Eq.~\ref{def:snd_gen}, called the \emph{Direct Parametrization} or DP, the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

%The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
To fit the CCF using a SN density shape, we use a least-squares algorithm and the following model:
%
\begin{eqnarray} \label{eq:3}
f_{CCF}(x_i) = \mathrm{C} - \mathrm{A} \times SN(x_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
\end{eqnarray}
%
where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, commonly referred to as the contrast, and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in velocity units (e.g. \ms).

@@

To evaluate the strength of the correlation between the estimated RV's and the different stellar activity indicators, we calculated the Pearson correlation coefficient, $R$, which in its general form is defined as:
%
\begin{equation}
R (x,y)= \frac{cov(x,y)}{\sigma(x)\sigma(y)},
\label{eq:Pearson:corr}
\end{equation}
%
where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.  A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\%$ confidence interval for $R$ when needed.

@@

When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM and to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
%Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case). The stellar activity correction we propose can therefore be written as:
%
\begin{equation}
RV_{\text{activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the error with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
The benefits of including a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}. 
This interaction term can account for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that each  variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.

@@

\jessi{Is the following paragraph needed?  Is any model selection actually carried out here?  It seems the model of Eq.~\ref{eq:RV:correction} is fit, and then the significance of the variables are discussed, but no attempts are really made to remove/add/step through the various model options.  The point about multicollinearity is probably good to keep though.} 
When working with a linear regression, there are several ways to select the variables to include in the model. While usually the stepwise technique is used \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction}, that accounts for stellar activity, is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible. This problem is known in statistics with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citet{belsley1991}. It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF. However, in the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ and therefore, the problem of multicollinearity is avoided. Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.

@@

For the simulations discussed below, a star similar to the Sun was modeled. The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on. \jessi{The previous sentence seems incomplete and I'm not sure how to update it.}
The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?  Also, why is it referenced?  Is the effective temperature supposed to be similar to the Sun?}, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011} are used. 
In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms and a resolution of 115'000.  \jessi{Is a resolution of ``115'000'' standard notation?  I'm not sure what it means.}
%, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RV's and the asymmetry parameters are displayed. In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RV's and, respectively, the asymmetry parameter or the width parameter.}
    \label{fig:faculae.corr}
\end{center}
\end{figure*}

>>>>

%\documentclass[referee]{aa}
%
\usepackage{pdflscape} % or {lscape}
\usepackage{natbib}
%\usepackage{lscape}
\usepackage{wasysym}
\usepackage[varg]{txfonts}
\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage[draft]{hyperref}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
\usepackage{longtable}

@@

\abstract
% Context, Aims, Methods, Results, Conclu (not mandatory)
{Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modeled CCF. Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
%
{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
%
{The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.}
%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels. In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.  We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
%
{When considering the real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach. 
This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
The estimated uncertainties in the estimated RVs using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF. }
{XXX \jessi{It looks like we still need to add conclusions here}}
%
%{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.  Furthermore, the estimated uncertainties on the RVs and the asymmetry parameter are smaller in the SN setting.}
%The correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations. Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals. The precision on the estimated set of RVs, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN). We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RVs and the the asymmetry parameter are smaller than the one estimated with the Normal fit.

@@

When working with radial-velocities data (RVs), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}. 
Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals that are above the meter-per-second precision \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
%
It is therefore mandatory to better understand stellar signals and to develop methods to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique. This is even more true now that instruments like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and the EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should reach the stability to detect such signals. However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging and false detections could plague the field.

@@

One of the most challenging stellar signal to characterize and to correct for is the signal induced by stellar activity. 
Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RVs variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b, Borgniet-2015}. 
In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}. 
However, on quiet GKM dwarfs, the main target for precise RVs measurements, stellar activity can induce signals of a few \ms. This corresponds physically to variations smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.
In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic or an observed stellar template \citep[][]{Baranne-1996,Pepe-2002a, Anglada-Escude-2012}. The result of this operation gives us the cross-correlation function (CCF).  
%The CCF gives the spectrum's cross-correlation with the template as the template is shifted according to different RVs.
%
To measure the Doppler-shift between different spectra and therefore to retrieve the RVs of a star as a function of time, the variations of the CCF barycenter are calculated. 
The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean. Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different moments of the CCF. Usually, the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density, and its asymmetry by calculating the CCF bisector and measuring the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.

@@

If an apparent RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}. 
%
It is therefore common now, that when fitting a Keplerian signal to a set of RVs to look for a planet, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
%
It is also common to add a Gaussian process to the model to account for the correlated noise induced by stellar activity. The hyperparameters of the Gaussian process can be trained on different activity indicators \citep{Haywood-2014,Rajpaul-2015} or directly on the RVs \citep{Faria-2016a}. It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated with the RVs but also for which we can obtain the best precision.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Figueira indicators of stellar activity + other}
Several indicators have been developed that are more sensitive to line asymmetry than the BIS SPAN. In \citet{Boisse-2011}, the authors develop $V_{span}$, which is the difference between the RV measured respectively by fitting a Normal density to the upper and the bottom part of the CCF. This CCF asymmetry parameter is shown to be more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
%
\citet{Figueira-2013} studied the use of new indicators, BIS-, BIS+, bi-Gauss and $V_{asy}$. The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger than when using BIS SPAN, therefore allowing the detection of lower levels of activity. They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any of the previously proposed asymmetry indictors.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Outline of paper}
The paper is organized as follow. In Sec.~\ref{sec:2} we introduce the SN density, describe its applicability for modeling the CCF, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF. 
%
In Sec.~\ref{sec:31} we propose an expanded linear model to correct for stellar activity signals in RVs, which extends the linear models previously proposed for this purpose \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}. 
%
In Sec.~\ref{sec:soap} the performance of the SN fit to the CCF is investigated using simulations coming from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}, followed by an analysis of real observations in Sec.~\ref{sec:4}.
%
Sec.~\ref{sec:5} considers derived error bars for the different estimated CCF parameters, and finally a discussion of the results and conclusions are included in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}, respectively.

@@

By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a clearer interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ provides an measure of the skewness of the SN. 
Along with the mean of the SN, we consider the median of the distribution as a measure of its barycenter.  See Table~\ref{tab:cp_values} for the medians of the SN densities displayed in Fig.~\ref{fig:SN.plot}.

%The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
%%
%\begin{equation} \label{eq:snmed}
%\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2}.
%\end{equation}
%

%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
\begin{center}
   \caption{CP values $(\mu, \sigma^2, \gamma)$ along with the median corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$. Values are rounded to three decimal places.}
   \label{tab:cp_values}
   \begin{tabular}{|ccccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$  & Median \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667  	& 	-0.672\\
0	&	 0.000 	&	1.000	&	 0.000 	& 	0.000\\
2	&	 0.714	&	 0.491	&	 0.454 	& 	0.655\\
6	&	 0.787	&	 0.381	&	 0.891 	& 	0.674\\
10	&	 0.794	&	 0.370	&	 0.956 	& 	0.674\\
\hline
   \end{tabular}

\end{center}
\end{table}
%
Further details about the parametrization from Eq.~\ref{def:snd_gen}, called the \emph{Direct Parametrization} or DP, the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

%The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
To fit the CCF using a SN density shape, we use a least-squares algorithm and the following model:
%
\begin{eqnarray} \label{eq:3}
f_{CCF}(x_i) = \mathrm{C} - \mathrm{A} \times SN(x_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
\end{eqnarray}
%
where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, some times referred to as the CCF contrast, and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in velocity units (e.g. \ms).

@@

To evaluate the strength of the correlation between the estimated RVs and the different stellar activity indicators, we calculated the Pearson correlation coefficient, $R$, which in its general form is defined as:
%
\begin{equation}
R (x,y)= \frac{cov(x,y)}{\sigma(x)\sigma(y)},
\label{eq:Pearson:corr}
\end{equation}
%
where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.  A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\%$ confidence interval for $R$ when needed.

@@

When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
%Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case). The stellar activity correction we propose can therefore be written as:
%
\begin{equation}
RV_{\text{activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the error with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
The benefits of including a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}. 
This interaction term can account for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that each  variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RVs is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.

@@

The proposed function defined in Eq.~\ref{eq:RV:correction} is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible. This problem is known in statistics with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citet{belsley1991}. In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore, the problem of multicollinearity is avoided. Note that we investigated the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CCF, however, those interaction were not relevant for accounting for stellar signal.

@@

For the simulations discussed below, a star similar to the Sun was modeled, with a solar disc of one solar radius seen equator-on, and with a stellar rotational period set to 25.0 days.
The stellar effective temperature is set to 5778 K
%(NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?  Also, why is it referenced?  Is the effective temperature supposed to be similar to the Sun?}
, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34 are used, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms\,and considering initial spectra with a spectral resolution of R=115'000.
%\jessi{Is a resolution of ``115'000'' standard notation?  I'm not sure what it means.}
%, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RVs and the asymmetry parameters are displayed. In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RVs and, respectively, the asymmetry parameter or the width parameter.}
    \label{fig:faculae.corr}
\end{center}
\end{figure*}
